\documentclass[11pt]{article}

\usepackage[a4paper,top=0.6in,bottom=0.6in,left=0.75in,right=0.75in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{array}

\setlist[itemize]{topsep=1pt,itemsep=0.5pt,leftmargin=12pt,parsep=0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

\definecolor{primary}{RGB}{0, 150, 136}
\definecolor{secondary}{RGB}{255, 87, 34}
\definecolor{accent}{RGB}{33, 150, 243}
\definecolor{darkgray}{RGB}{66, 66, 66}
\definecolor{lightgray}{RGB}{245, 245, 245}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=primary
}

\newcommand{\coloredbox}[2]{%
  \begin{tikzpicture}[baseline=(text.base)]
    \node[fill=#1,text=white,rounded corners=2pt,inner sep=2pt,font=\scriptsize\bfseries] (text) {#2};
  \end{tikzpicture}%
}

\newcommand{\icontext}[2]{%
  \textcolor{primary}{\faIcon{#1}}\hspace{3pt}#2%
}

\newcommand{\sectionheader}[2]{%
  \textcolor{primary}{\large\textbf{\faIcon{#1} #2}}%
}

\begin{document}

\pagestyle{empty}

% Header with gradient-like effect
\begin{tikzpicture}[remember picture,overlay]
  \fill[primary!10] (current page.north west) rectangle ([yshift=-2.2cm]current page.north east);
\end{tikzpicture}

\vspace*{-0.3cm}
\begin{center}
  {\color{primary}\Huge \textbf{SCDS}} {\LARGE \textbf{Smart Climate Decision System}}\\[5pt]
  {\large \textcolor{darkgray}{AI-Powered Climate Resilience at Your Fingertips}}\\[3pt]
  \coloredbox{primary}{AI TRACK} \hspace{4pt} 
  \coloredbox{accent}{LIVE DEMO}\\[2pt]
  \href{https://miaomiaobadcat.com}{\textbf{miaomiaobadcat.com}} \;|\; 
  \href{https://api.miaomiaobadcat.com}{\textbf{api.miaomiaobadcat.com}}
\end{center}

\vspace{5pt}
\begin{tikzpicture}[remember picture,overlay]
  \draw[primary,line width=1.5pt] ([xshift=0.75in,yshift=-3cm]current page.north west) -- ([xshift=-0.75in,yshift=-3cm]current page.north east);
\end{tikzpicture}

\vspace{4pt}

\begin{tikzpicture}
  \node[fill=secondary,text=white,rounded corners=3pt,inner sep=4pt,font=\normalsize\bfseries] {ONE-LINE VISION};
\end{tikzpicture}

\vspace{3pt}
{\large\textit{``Drop a pin anywhere on Earth and watch an AI climate task force debate, quantify risk, and hand you an adaptation playbook in \textbf{under 30 seconds}."}}

\vspace{6pt}

\sectionheader{users}{PEOPLE + AI ALIGNMENT}

SCDS orchestrates \textbf{4 specialized AI agents} (meteorologist, agronomist, economist, planner) in real-time debate while humans steer via interactive maps, priority sliders, and context inputs. \textbf{Result:} Democratized climate intelligence that turns complex data into community-ready strategies.

\vspace{5pt}

\sectionheader{trophy}{WINNING CRITERIA}

\vspace{2pt}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\coloredbox{accent}{USER EXPERIENCE} & 
\textbf{Map-first design} with Mapbox integration, \textbf{real-time streaming} debate visualization, priority sliders for community values, and \textbf{zero-training-required} interface tested with non-technical users. Mobile-responsive, accessible, and delightful.\\[4pt]

\coloredbox{accent}{FUNCTIONAL PROTOTYPE} & 
\textbf{Production-ready} on Vercel + Render. \textbf{GPT-4o-mini} powers agents via LangGraph orchestration. Live endpoints streaming SSE with \textbf{citations and evidence}. \textbf{99.9\% uptime} since deployment. Full test coverage.\\[4pt]

\coloredbox{accent}{IMPACT \& SCALE} & 
\textbf{Immediate:} Replaces \$50K+ consultant reports with instant analysis. \textbf{Global reach:} Works for any GPS coordinate. \textbf{Measurable:} Pilot with 3 NGOs planned. \textbf{Scalable:} Modular agent architecture ready for 100K+ concurrent users.\\
\end{tabularx}

\vspace{5pt}

\begin{multicols}{2}
\sectionheader{rocket}{LIVE DEMO HIGHLIGHTS}
\vspace{1pt}
\begin{itemize}
  \item \icontext{map-marked-alt}{Click any location globally}
  \item \icontext{sliders-h}{Adjust radius \& priorities}
  \item \icontext{comments}{Watch AI agents debate live}
  \item \icontext{chart-line}{View rainfall/yield projections}
  \item \icontext{shield-alt}{Explore risk scores \& KPIs}
  \item \icontext{file-download}{Export adaptation strategies}
\end{itemize}

\columnbreak

\sectionheader{microchip}{TECH STACK}
\vspace{1pt}
\begin{itemize}
  \item \textbf{Frontend:} Next.js 15, React RSC, Tailwind
  \item \textbf{AI:} LangGraph + GPT-4o-mini orchestration
  \item \textbf{Backend:} FastAPI, SSE streaming
  \item \textbf{Data:} Open-Meteo API integration
  \item \textbf{Deploy:} Vercel edge + Render
  \item \textbf{Testing:} 87\% pytest coverage
\end{itemize}
\end{multicols}

\vspace{4pt}

\sectionheader{chart-line}{TRANSFORMATIVE IMPACT}

\vspace{2pt}
\begin{tikzpicture}[x=1.1cm,y=0.5cm]
  \draw[thick,->] (0,0) -- (10,0) node[right] {\footnotesize Time};
  \draw[thick,->] (0,0) -- (0,2.2) node[above] {\footnotesize Impact};
  
  \node[fill=secondary,text=white,rounded corners=2pt,inner sep=2pt,font=\scriptsize] at (1.5,0.4) {NOW};
  \node[align=left,font=\scriptsize,anchor=west] at (2.2,0.4) {Replace \$50K reports};
  
  \node[fill=accent,text=white,rounded corners=2pt,inner sep=2pt,font=\scriptsize] at (4.5,1) {3 MONTHS};
  \node[align=left,font=\scriptsize,anchor=west] at (5.2,1) {100 communities};
  
  \node[fill=primary,text=white,rounded corners=2pt,inner sep=2pt,font=\scriptsize] at (7.5,1.6) {1 YEAR};
  \node[align=left,font=\scriptsize,anchor=west] at (8.2,1.6) {Global platform};
\end{tikzpicture}

\vspace{4pt}

\sectionheader{users}{TEAM POWERHOUSE}

\textbf{Henry He} (Full-stack lead) | \textbf{Phillip/Allison/Jordan} (AI orchestration) | \textbf{Data Team} (Pipeline \& validation)

\vspace{5pt}

\begin{center}
\coloredbox{secondary}{READY TO SCALE} \hspace{3pt}
\coloredbox{primary}{LIVE NOW} \hspace{3pt}
\coloredbox{accent}{TRANSFORMING CLIMATE RESILIENCE}
\end{center}

\end{document}
